Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2015-10-31 draft.tex
modify lemma 1 and proof for change to initial conditions

\begin{quotation}
\noindent \textit{{\bf Lemma 1:} Conditions 1 and 2 are sufficient for status quo to be the outcome of Stage 3 in any period.} 
\end{quotation}

@@

{\bf Proof of Lemma 1} \\
Recall that the upper case notation represents payoffs gross of investments by the outside players. Without loss of generality, consider the incentives to deviate for player $s$ in period $t$ given that the other three players play their equilibrium actions. Given the stationary equilibrium actions, playing Status Quo will lead to $Q_{st} \ \forall t$, so the continuation value is $\frac{Q_{st}}{1-\delta}$. Player $s$'s continuation value from the one-shot deviation to Cede, which leads to an absorbing state with payoff $L_{st}$ in each period, is $\frac{L_{st}}{1-\delta}$. The one-shot deviation to fight results in the war lottery, with a cost of $-\zeta_s$, $W_s$ forever with probability $p_1$, and $L_s$ forever with probability $1-p_1$. Thus the continuation value is $\zeta_s +\frac{W_{st}(p_1)+ L_{st}(1-p_1)}{1-\delta}$.

In order for player $s$ to play Status Quo, it must be that the continuation value from Status Quo is higher than both that from playing Cede (Condition 1) and Fight (Condition 2). The argument for player $g$ is symmetric. \hfill $\blacksquare$
\\
\\
\noindent {\bf Proof of Lemma 2} \\
In the status quo, we have $U_{pt}^{SQ}= -R_p^{SQ}$ and $U_{ct}^{SQ}= -R_c^{SQ}$. If the outcome is reunification, payoffs in this absorbing state in the period in which the investment is made are $U_{pt}^{RU}= -\alpha -R_p^{RU}$ and $U_{ct}^{RU}= \beta -R_c^{RU}$ where $SQ$ and $RU$ distinguish investments under the status quo and reunification scenarios respectively.

>>>>

\begin{quotation}
\noindent \textit{{\bf Lemma 1:} $Q_{it} \geq L_{it}$ and $\frac {Q_{it}}{1-\delta} \geq  -\zeta_i+\frac{W_{it}(p_{1i}) + L_{it}(1-p_{1i})}{1-\delta}$ for $i \in \left\{g,s\right\}$ are sufficient for status quo to be the outcome of Stage 3 in period $t \ \forall t$.} 
\end{quotation}

@@

{\bf Proof of Lemma 1} \\
Recall that the upper case notation represents payoffs gross of investments by the outside players. Without loss of generality, consider the incentives to deviate for player $s$ in period $t$ given that the other three players play their equilibrium actions. Given the stationary equilibrium actions, playing Status Quo will lead to $Q_{st} \ \forall t$, so the continuation value is $\frac{Q_{st}}{1-\delta}$. Player $s$'s continuation value from the one-shot deviation to Cede, which leads to an absorbing state with payoff $L_{st}$ in each period, is $\frac{L_{st}}{1-\delta}$. The one-shot deviation to fight results in the war lottery, with a cost of $-\zeta_s$, $W_s$ forever with probability $p_1$, and $L_s$ forever with probability $1-p_1$. Thus the continuation value is $-\zeta_s +\frac{W_{st}(p_1)+ L_{st}(1-p_1)}{1-\delta}$.

Given that the continuation value from Status Quo is higher than both that from playing Cede and Fight, player $s$ will play Status Quo. The argument for player $g$ is symmetric. \hfill $\blacksquare$
\\
\\
\noindent {\bf Proof of Lemma 2} \\
In the status quo, we have $U_{pt}^{SQ}= -R_p^{SQ}$ and $U_{ct}^{SQ}= -R_c^{SQ}$. If the outcome is reunification, payoffs in this absorbing state in the period in which the investment is made are $U_{pt}^{RU}= -\alpha -R_p^{RU}$ and $U_{ct}^{RU}= \beta -R_c^{RU}$ where $SQ$ and $RU$ distinguish investments under the status quo and reunification scenarios respectively.
